---
title: "Xabier Vázquez-Campos's CV"
author: "`r paste0(params$author, ', ', params$author_title)`"
date: "`r Sys.Date()`"
params:
  author: "Xabier Vázquez-Campos"
  aliases: "aliases.txt"
  author_title: "PhD"
  position: "Computational biologist | Environmental microbiologist"
  long_cv: TRUE
  sheet_is_publicly_readable: true
  data_location: "https://docs.google.com/spreadsheets/d/16xpf0YnVbZdzgDBwobBuidjpI7SW8jVQepWfpfql_pE/edit?usp=sharing"
  repository: "https://github.com/xvazquezc/datadrivencv-academic"
  pub_location: "./input_files/"
  pdf_mode: TRUE
output:
  pagedown::html_resume:
    keep_md: FALSE
    css: 
      - 'css/fontawesome-free-6.2.1-web/css/all.min.css'
      - 'resume'
      - 'css/dd_cv.css'
      - 'https://cdn.rawgit.com/jpswalsh/academicons/master/css/academicons.min.css'
    self_contained: true
knit:
  pagedown::chrome_print
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
library(fontawesome)
source("code/cv_printing_functions.R")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = params$data_location,  
  pdf_mode = params$pdf_mode,
  long_cv = params$long_cv
)

PUB <- create_PUB_object(
  data_location = params$pub_location,
  aliases = paste0(params$pub_location, params$aliases),
  pdf_mode = params$pdf_mode,
  long_cv = params$long_cv
)
```


```{r pdf_eval}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r download_cv}
if (params$long_cv == TRUE) {
  glue::glue(
    "[<i class='fas fa-download'></i> Download a PDF of this CV]({params$repository}/raw/main/cv_long.pdf)"
  )
} else {
  glue::glue(
    "[<i class='fas fa-download'></i> Download the extended version of this CV]({params$repository}/raw/main/cv_long.pdf)"
  )
}
```


Contact {#contact}
--------------------------------------------------------------------------------

```{r contact_info}
CV %>% print_contact_info()
```


<!-- Skills {#skills} -->
<!-- -------------------------------------------------------------------------------- -->

```{r skill_list}
CV %>% print_skill_list("comp_bio")
```


```{r skill_coding}
CV %>% print_skill_list("coding")
```

<!-- Language Skills {#skills} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- CV %>% print_skill_bars() -->
<!-- ``` -->



Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

The source code is available on my [datadrivencv-academic repository](`r params$repository`).

Last updated on `r Sys.Date()`.


<!-- Second sidebar {.aside .extra-sidebar} -->
<!-- ================================================================================ -->

<!-- ::: aside -->
<!-- ```{r skill_lang} -->
<!-- CV %>% print_skill_list("language") -->
<!-- ``` -->
<!-- ::: -->


Main
================================================================================

`r paste0(params$author, ', ', params$author_title)` {#title}
--------------------------------------------------------------------------------

### `r params$position`

<!-- ```{r} -->
<!-- # Note the special double pipe so we modify the CV object in place -->
<!-- CV %<>% print_text_block("intro")  -->
<!-- ``` -->


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r education}
CV$entries_data %<>% print_section('education', glue_template = "default")
```


Research Experience {data-icon=laptop}
--------------------------------------------------------------------------------

```{r research_positions}
CV$entries_data %<>% print_section('research_positions', glue_template = "default")
```


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

## Courses {data-icon=person-chalkboard #subtitle_teach_courses}

<!-- ```{r} -->
<!-- CV %<>% print_text_block('teaching_experience_aside') -->
<!-- ``` -->

```{r courses}
CV$teaching %<>% print_section('courses', glue_template = "teaching")
```


## Invited lectures {data-icon=chalkboard-user #subtitle_teach_invited}

```{r invited_lectures}
CV$teaching %<>% print_section('invited_lectures', glue_template = "teaching")
```


## Workshops {data-icon="users-gear" #subtitle_teach_ws}

```{r workshops}
CV$teaching %<>% print_section('workshops', glue_template = "teaching")
```


## Supervision {data-icon=user-pen #subtitle_super}

```{r aside_supervision}
CV %<>% print_text_block_aside("supervision")
```


```{r supervision}
CV$supervision %<>% print_section('formal', glue_template = "supervision")
```



Grants {data-icon=hand-holding-dollar}
--------------------------------------------------------------------------------

```{r grants}
CV$grants_awards %<>% print_section('grants', glue_template = "grants")
```


Awards {data-icon=award}
--------------------------------------------------------------------------------

```{r awards}
CV$grants_awards %<>% print_section('awards', glue_template = "grants")
```



```{r training_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  'Training and professional development {data-icon=user-plus}\n',
  '--------------------------------------------------------------------------------',
  .open = "{{", .close = "}}")
```

```{r training_summary, eval = (params$long_cv == TRUE)}
CV %<>% print_text_block_aside("training")
```

```{r training_courses_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  '## Courses {data-icon=book-open-reader #subtitle_train_course}',
  .open = "{{", .close = "}}")
```

```{r training_courses, eval = (params$long_cv == TRUE)}
CV$training %<>% print_section('course', glue_template = "training")
```

```{r training_ws_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  '## Workshops {data-icon="user-gear" #subtitle_train_ws}',
  .open = "{{", .close = "}}")
```

```{r training_workshops, eval = (params$long_cv == TRUE)}
CV$training %<>% print_section('workshop', glue_template = "training")
```

```{r fix_paging, eval = (params$long_cv != TRUE), results = "asis"}
glue::glue(
  '\\newpage',
  .open = "{{", .close = "}}")
```


Publications {data-icon="book"}
--------------------------------------------------------------------------------

```{r preprints_eval}
# preprint section only if there is some active preprint AND it's long CV
preprint_eval <- params$long_cv & length(PUB[["preprints"]]) != 0
```

```{r preprints_title, eval = preprint_eval, results = "asis"}
glue::glue(
  '## <i class="ai ai-biorxiv"></i> Pre-prints {#subtitle_preprint}',
  .open = "{{", .close = "}}")
```

```{r preprints, eval = preprint_eval}
PUB$preprints %<>% print_section('preprints', glue_template = "preprints")
```

```{r under_review_eval}
#only write section under_review if there is any paper in that biblio file AND it's long CV
under_review_eval <- params$long_cv & !is.null(PUB[["under_review"]])
```

```{r under_review_title, eval = under_review_eval, results = "asis"}
glue::glue(
  '## Under review {data-icon=magnifying-glass-chart #subtitle_under_review}',
  .open = "{{", .close = "}}")
```

```{r under_review, eval = under_review_eval}
PUB$under_review %<>% print_section('under_review', glue_template = "under_review")
```


```{r journals_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  '## Journal articles {data-icon="file-alt" #subtitle_journals}',
  .open = "{{", .close = "}}")
```

```{r peer_reviewed}
if (params$long_cv != TRUE) {
  #text block for short CV
  CV %<>% print_text_block_aside("pubs_shortcv")
}

PUB$peer_reviewed %<>% print_section('peer_reviewed', glue_template = "pubs")
```


```{r reports_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  '## Technical Reports {data-icon="file-invoice" #subtitle_techrep}',
  .open = "{{", .close = "}}")
```

```{r reports, eval = (params$long_cv == TRUE)}
PUB$reports %<>% print_section('reports', glue_template = "reports")
```


Conference contributions {data-icon="users"}
--------------------------------------------------------------------------------

```{r conferences_shortcv, eval = (params$long_cv != TRUE)}
#short conf contributions for short CV
CV %<>% print_text_block_aside("conf_shortcv")

PUB$conferences %<>% print_section('conferences', glue_template = "conferences")
```


```{r conf_oral_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  '## Oral presentations {data-icon=person-chalkboard #subtitle_oral}',
  .open = "{{", .close = "}}")
```

```{r conf_oral, eval = (params$long_cv == TRUE)}
PUB$conf_oral %<>% print_section('conf_oral', glue_template = "conferences")
```


```{r conf_poster_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  '## Posters {data-icon=clipboard-user #subtitle_posters}',
  .open = "{{", .close = "}}")
```

```{r conf_poster, eval = (params$long_cv == TRUE)}
PUB$conf_poster %<>% print_section('conf_poster', glue_template = "conferences")
```


```{r conf_coauth_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  '## Co-authored contributions {data-icon=handshake #subtitle_coauth}',
  .open = "{{", .close = "}}")
```

```{r conf_coauth, eval = (params$long_cv == TRUE)}
#aside
CV %<>% print_text_block_aside("conf_coauth")
#main
PUB$conf_coauth %<>% print_section('conf_coauth', glue_template = "conferences")
```


```{r invited_talks_title, eval = (params$long_cv == TRUE), results = "asis"}
glue::glue(
  'Invited talks {data-icon=person-chalkboard}\n',
  '--------------------------------------------------------------------------------',
  .open = "{{", .close = "}}")
```

```{r invited_talks, eval = (params$long_cv == TRUE)}
PUB$invited_talks %<>% print_section('invited_talks', glue_template = "invited_talks")
```


Service {data-icon=handshake-angle}
--------------------------------------------------------------------------------

```{r service}
CV$service %<>% print_section('membership_inst', glue_template = "service_gen")
CV$service %<>% print_section('membership_prof', glue_template = "service_gen")
CV$service %<>% print_section('service_conf', glue_template = "service_gen")
```


```{r reviewer}
CV$service %<>% print_section('reviews', glue_template = "reviews")
```


```{r aside_reviewer}
CV %<>% print_text_block_aside("reviewer")
```


```{r}
CV %<>% print_links()
```
